PK object batch mode trial

### 2023-09-12 data-raw/batchMode_trial_gpm.Rmd
Removed a browser() call in plot.pk() and added definitions for time units

```{r single_fit}
# Pooled
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

@@

  myRMSE_all <- rmse(obj,
                     rmse_group = vars(Route, Media, Dose),
                     use_scale_conc = FALSE) %>% 
    inner_join(winning_model) %>%
    dplyr::group_by(!!!obj$data_group, model, method) %>%
    dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4),
                     median_MSE = median(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4))
  browser()
  my_df <- left_join(fold_errors_all, r2_df) %>%
    inner_join(myAIC) %>%
    inner_join(myRMSE_all) %>%
    mutate(Options = pk_name, .before = Chemical) %>%
    dplyr::select(!c("model_1comp", "model_2comp", "model_flat"))

@@

### Plotting for all (2GB file)
pdf(file = paste0(Sys.getenv("FIG_DIR"),
              "DoseNormalized_Joint_AllFits.pdf"))
for (i in 1:nrow(pl)) {
  print(pl$final_plot[[i]])
}
dev.off()

>>>>

```{r single_fit}
# Pooled
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

@@

  myRMSE_all <- rmse(obj,
                     rmse_group = vars(Route, Media, Dose),
                     use_scale_conc = FALSE) %>% 
    inner_join(winning_model) %>%
    dplyr::group_by(!!!obj$data_group, model, method) %>%
    dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4),
                     median_MSE = median(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4))

  my_df <- left_join(fold_errors_all, r2_df) %>%
    inner_join(myAIC) %>%
    inner_join(myRMSE_all) %>%
    mutate(Options = pk_name, .before = Chemical) %>%
    dplyr::select(!c("model_1comp", "model_2comp", "model_flat"))

@@

### Plotting for all (2.5MB file)
pl <- plot(my_pk, n_interp = 8, use_scale_conc = TRUE)
pdf(file = paste0(Sys.getenv("FIG_DIR"),
              "DoseNormalized_Pooled_AllFits.pdf"),
    height = 6, width = 10)
for (i in 1:nrow(pl)) {
  print(pl$final_plot[[i]])
}
dev.off()

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "DoseNormalized_DTXSID8025337.png"),
       units = "in",
       height = 5.05,
       width = 5.55,
       dpi = 200)
